---
title: "FARS Functions Vignette"
author: "Cody Schulz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette describes the R package 'samplePackage2'. The package can read in, summarize, and map 2013-2015 motor vehicle accident data from the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars) (FARS).

## Reading in Data

samplePackage2 has several ways to read in data. The first is to use fars_read() and make_filename() in conjunction. For example, to read in data from 2013, use:
```{r}
library(samplePackage2)
fars_read(make_filename(2013))
```

To read in multiple years of data, supply a vector of years to fars_read_years:
```{r}
fars_read_years(c(2013, 2014, 2015))
```

Notice that the output of the first call was a single data frame, but the output of the second was a list of data frames.

## Summarizing Data

To use the package's built-in summarizing functions, simply call fars_summarize_years with a vector of years whose summary is desired. fars_summarize_years returns a data table with the number of accidents per month occurring in the years given.
```{r}
fars_summarize_years(c(2013, 2014))
```

## Mapping Data

To use the package's built-in mapping functions, provide fars_map_state with a year and state number. The function will then output a plot of each accident in that state in the given year. The state number corresponds to the alphabetized listing of states (1 = Alabama, 56 = Wyoming).

```{r}
fars_map_state(16, 2013)
```
